---
title: Applications of Computational Statistics Methods in Equity-linked Insurance
  Pricing
author: "Peng Jin, Guanzhong Tao, Haoen Cui, Dayu Yao, Yuan Zhong"
date: "November 13, 2017"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
    df_print: paged
runtime: shiny
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
options(scipen = 1, digits = 4, width = 80)
library(knitr)
library(kableExtra)
library(quantmod)
library(reshape2)
opts_chunk$set(echo=FALSE,
               cache=TRUE, autodep=TRUE, cache.comments=FALSE,
               message=FALSE, warning=FALSE)
```

###Data Preparation 

####Data Import (Mortality Table)

The data was download from The Human Mortality Database, a nonprofit organization that provides mortality data for researchers, students, and policy analysts. There are 39 countries' data available on the website, but this project is mainly focused on the USA.

```{r,echo=T}
male<-read.table("/Users/Peng/Desktop/STAT428/STAT-428-Final-Project/mltper_1x1.txt",skip=1,header=T)
female<-read.table("/Users/Peng/Desktop/STAT428/STAT-428-Final-Project/fltper_1x1.txt",skip=1,header=T)
both<-read.table("/Users/Peng/Desktop/STAT428/STAT-428-Final-Project/bltper_1x1.txt",skip=1,header=T)
```

####Data Structure and Variable explanation

```{r,echo=T}
head(both)##Data Structure
names(both)##Variable Names 
```

```{r,echo=FALSE}
text_tbl <- data.frame(
  Variables = names(both),
  Explanation = c("Year or range of years (for both period & cohort data)","Age group for n-year interval from exact age x to just before exact age x+n, where n=1, 4, 5, or infinite(open age interval)","Central death rate between ages x and x+n","Probability of death between ages x and x+n","Average length of survival between ages x and x+n for persons dying in the interval","Number of survivors at exact age x, assuming l(0) = 100,000","Number of deaths between ages x and x+n","Number of person-years lived between ages x and x+n","Number of person-years remaining after exact age x","Life expectancy at exact age x (in years)"
  )
)
kable(text_tbl, "html") %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold = T, border_right = T,border_left=T) %>%
  column_spec(2, width = "30em",border_right = T,background='pink')
```

####Data Import (Stock Index)

The data was downloaded from "Yahoo Finance". The equity-linekd insurnace products are mainly based on the three biggest indices in the US: NASDAQ, S&P 500, and Dow Jones.

```{r,echo=TRUE}
dow_jones<-read.csv("/Users/Peng/Desktop/STAT428/STAT-428-Final-Project/Dow Jones.csv")
nasdaq<-read.csv("/Users/Peng/Desktop/STAT428/STAT-428-Final-Project/NASDAQ.csv")
s_p500<-read.csv("/Users/Peng/Desktop/STAT428/STAT-428-Final-Project/S&P 500.csv")
```

####Data Structure and Variable explanation
```{r,echo=TRUE}
head(nasdaq)##Data Structure
names(nasdaq)##variable names
```
```{r,echo=FALSE}
text_tbl <- data.frame(
  Variables = names(nasdaq),
  Explanation = c("Stock Timestamp","Open Price","Highest Price","lowest Price","Closing Price","Adjusted Closing Price","Trading Volume"
  )
)
kable(text_tbl, "html") %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold = T, border_right = T,border_left=T) %>%
  column_spec(2, width = "30em",border_right = T,background='pink')
```

###Method Explannation

```{r,cache=FALSE,echo=FALSE}
#mortality function
mortality<-function(age,year,length,gender){
  if((age+length)>max(as.numeric(levels(male$Age)),na.rm = TRUE)){return("invalid inputs")}
  a<-which(gender$Age==age & gender$Year==year)
  tqx<-(gender$lx[a]-gender$lx[a+length])/gender$lx[a]
  return(tqx)
}
```

```{r,cache=FALSE}
library(shiny)
library(ggplot2)
ui <- fluidPage(
  titlePanel("Guaranteed Minimum Maturity Benefit"),
  
  sidebarLayout(
    sidebarPanel(
      helpText("Select a stock to examine. 
        Information will be collected from Yahoo finance."),
      
      textInput("symb", "Symbol", "SPY"),
      
      dateRangeInput("dates", 
                     "Insured Period",
                     start = "2013-01-01", 
                     end = as.character(Sys.Date())),
      
      numericInput("num", "Premium Invested", value = 100),
      
      checkboxInput("log","Plot y Axis on Log Scale"),
      
     checkboxInput("St", "Real Time Stock Value (St)", 
                    value = TRUE),
      checkboxInput("Ft","Market Value of the policy holder's subaccounts (Ft)",
                    value = FALSE),
     checkboxInput("Gt","Guranteed Value (Gt)", value=FALSE)),
  
    mainPanel(plotOutput("plot"),h3(textOutput("final")))
  )
)
# Server logic
server <- function(input, output) {
  
  dataInput <- reactive({
      a_1<-getSymbols(input$symb, src = "yahoo",
                         from = input$dates[1],
                         to = input$dates[2],
                         auto.assign = FALSE)
      a<-as.data.frame(a_1)
      n<-length(a[,1])
      Ft_col<-Gt_val<-numeric(n)
    for (i in 1:length(Ft_col)){
      Ft_col[i]<-input$num*(a[,2][i]/a[,2][1])*exp(-i*0.02/365)
      Gt_val[i]<-max(Ft_col[i],input$num*exp(i*0.01/365))
    }
    
    ind<-c()
    if(input$St==TRUE){ind<-c(ind,2)}
    if(input$Ft==TRUE){ind<-c(ind,3)}
    if(input$Gt==TRUE){ind<-c(ind,4)}
    ind<-c(1,ind)
    dates=index(a_1)
    St=a[,4]
    Ft=Ft_col
    Gt=Gt_val
    all_data<-data.frame(dates,St,Ft,Gt)[,ind]
    final_payout<-max(Gt_val[n],Ft_col[n])
    if(input$log==FALSE){
      list(all_data,final_payout)}
    else{
      list(data.frame(dates,log(St),log(Ft),log(Gt))[,ind],final_payout)
    }
  })
  output$plot <- renderPlot({
    df <- melt(dataInput()[[1]], "dates")
    X<-as.Date(dataInput()[[1]][n,1])
    Y<-dataInput()[[2]]
    df2<-data.frame(x=X,y=Y)
    ggplot(df, aes(x=dates, y=value, color=variable)) + 
      geom_line()
      
     
  })
  output$final<-renderPrint({
    
    paste("Your Initial Premium Investment is",input$num," and your account balance will be",round(dataInput()[[2]],2),"after the designated period")
  })
  
}

# Run the app
shinyApp(ui, server)
```
