---
title: "Code Structure"
author: "Haoen Cui, hcui10"
output: 
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sources of Risks

### Overview
We consider three sources of `risk`: decrements, investment return, interest rate. We allow them to have some dependence, but will not model them jointly. For each type of risk, we will have three main methods:  

1. `risk.clean.data(raw.data)`  
    * Args: raw input data   
    * Return: cleaned data for the following functions to use  
2. `risk.calibrate(hist.data, model)`   
    * Args: cleaned historic data, model type  
        + each model type should have its helper function `risk.calibrate.model(hist.data)`  
    * Return: a list of estimated parameters and accuracy estimates (e.g. using bootstrap methods)  
3. `risk.predict(model, param, max.length, n = 100)`  
    * Args: model type, associated parameters , time horizon for simulaiton, and number of simulation to run
        + can have a helper function `risk.simulate(model, param, max.length)` to just simulate one realization  
    * Return: a list of simulation result up to `t.now + max.length` containing a matrix of `n` simulations using the `model` type and associated `param`   
4. other helper functions as necessary

Notes:   

* all time units should be in years. For example, $\frac{1}{12}$ is 1 month  
* functions should be well-documented  
```{r}
# use tidy formats, e.g. dplyr, tibbles/data.frame
# require("tidyverse")

# function definition
some.function <- function(...) {
  # short description of the funciton
  # 
  # Args:
  #   arg1: meaning of arg1
  #
  # Return:
  #   ele1: meaning of ele1
  
  #... some code ...
  
  return(list())
}
```

### Decrement

* The second funciton will be modified, `risk.calibrate(hist.data, source, model)` should take in one more parameter `source` from `c("mortality", "lapse", "annuitization")` where the associated models are `c("life-table")`, `c("const")`, and `c("const")`. 

### Investment Return

* `risk.clean.data(raw.data)` should take care of dividends and splits  
* Assume stock return follows a grometric Brownian motion for now  

### Interets Rate

* Only supports Vasicek model for now  
* The third funciton will be modified, `risk.predict(model, param, max.length, n = 100)` should return predictions of short-term rate, yield curve, and aero-coupon bond price  

## Methods in STAT 428

Naming convention: `STAT428.function.name(...)`.  

### Random Number Generation 
`STAT428.rdist(n, method, method.param)` accepts `n` as output sample length, `method` as method type (e.g. `"MCMC"`) and, `method.param` as associated parameters, then returns a generated sample of length `n` using the method specified. Methods should at least include the following:  

* Inverse Transformation Method  
* Acceptance-Rejection Method  
* Markov Chain Monte Carlo
```{r}
rdist=function(n,method,method.parameter){
  if (method=="inverse"){
    u=runif(n)
    x=method.parameter$invCDF(u)
    return(x)
  }
  else if (method=="ar"){
    k=0
    y=numeric(n)
    if (c=="auto"){
      generated_x=method.parameter$rproposal(10000)
      fxgx=method.parameter$dtarget(generated_x)/method.parameter$dproposal(generated_x)
      c=max(fxgx)
    }else{c=method.parameter$c}
    while(k<n){
      u=runif(1)
      x=method.parameter$dproposal(method.parameter$rproposal(1))#function that generate x from proposal
      if (dtarget(x)/(c*dproposal(x))>u){
        k=k+1
        y[k]=x
      }
    }
    return(y)
  }
  else if (method=="mcmc"){
    x = numeric(n)
    x[1] = method.parameter$rproposal(1,df=1)#might need to specify chisq, t, or other ones 
    u = runif(n)
    for (i in 2:n) { 
    xt = x[i-1]
    y = method.parameter$rproposal(n, df=xt)
    num = method.parameter$dtarget(y) * method.parameter$dproposal(xt, df = y) 
    den = method.parameter$dtarget(xt) * method.parameter$dproposal(y, df = xt) 
    if (u[i] <= num/den) x[i] = y else {
      x[i] = xt
      }
    }
    return(x)
  }
  }
```

### Bootstrap
Use `boot::boot()` and/or `broom::bootstrapping()`

### Optimization
Depends on needs of parameter estimation of the three risks. Potential methods are listed below:  

* solve $f(x)=0$ using root bracketing (e.g. bisection method, Brent’s method)   
* solve $f(x)=0$ using iterative methods (e.g. Newton-Raphson method)  
* optimize $\min_{x \in \mathbb{R}^n} f(x)$ using iterative methods (e.g. Newton's method)  
* parameter estimation using E-M algorithm  
